---
title: "Lab 01 - Hello R"
author: "Noah Booker"
date: "1/28/25"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

1846 rows, 3 columns; 3 variables: dataset, x, and y.

### Exercise 2

Plotting the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
From viewing the data visualization, we see that it wouldn't make sense to calculate a correlation between x and y in this data set since there is not a linear relationship. However, if we do calculate a correlation, we get r = -0.0645.


### Exercise 3

Plotting the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
    filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
    geom_point()
```

Calculating the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
    summarize(r = cor(x, y))
```
Although the star data looks very different from the dino data, x and y have almost the same correlation.


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


